\chapter{Code of Conduct}
\label{cha:code-of-conduct}

This Code shall be the example by which we, as brothers, commit ourselves for
the purpose of becoming Men of Principle.
A brother shall be considered active and in good standing if he has met all of
these expectations.

\section{Brotherhood Obligations}
\label{sec:brotherhood-obligations}

Each brother shall always uphold the Principles and Obligations of the Beta
Theta Pi Fraternity.

\section{Financial Obligation}
\label{sec:financial-obligation}

Each inducted member is required to sign a promissory note, written by the
Finance Chairman and approved by the Executive Board, at the end of each
semester.
Each brother shall always fulfill his financial obligations within two weeks of
being billed; and if not possible, the brother shall work out a payment plan
with the Finance Chairman.
Bills shall include, but are not limited to, the following:

\begin{itemize}
	\item Active member local dues
	\item New Member dues
	\item General fraternity dues
	\item Interfraternity council dues
	\item Housing fee
\end{itemize}

If a brother is not able to meet the financial obligation he has the option of
becoming financially inactive as per the Financial Inactivity Bylaw.

\section{Academic Success}
\label{sec:academic-success}

Each brother shall always strive to maintain at least a 2.8 GPA, if a brother is
unable to achieve this he will be placed on the Academic Assistance Plan.

\section{Active Participation}
\label{sec:active-participation}

Active brothers are required to attend the following events:

\begin{itemize}
	\item Kickoff and mid-year retreats
	\item Two of the three community service events per term as defined
		in Section~\ref{sec:community-service}
	\item All ritual events
	\item All chapter meetings
	\item All committee meetings
	\item Brotherhood education sessions
	\item Beta Philanthropy events
	\item Beta Fundraising events
\end{itemize}

In addition, all members of the Executive Board are required to attend all
Executive Board meetings.
Excusals and other participation issues will be addressed according to
Item~\ref{cha:attendance-and-accountability-policy}: Attendance and
Accountability Policy.

\section{Community Service}
\label{sec:community-service}

\subsection{Hours to Complete}
\label{sec:hours-to-complete}

Each active brother shall complete a total of 10 hours per semester.
If a brother is inactive for a term within the semester due to off campus
IQP/MQP, co-op, medical leave or other reason determined legitimate by Kai, that
brother’s semesterly requirement is reduced by 5 hours per term.
Brothers are
also allowed to complete all of their total semester requirement independent
from Beta pending approval from the Community Service Chair.
The Community Service Chair, as outlined in
Section~\ref{sec:duties-of-the-community-service-chairman}, must approve of the
service and the brother is responsible for providing the chair with proof of
completion.

\subsection{Duties of the Community Service Chairman}
\label{sec:duties-of-the-community-service-chairman}

The Community Service Chair will be appointed at least two weeks before the end
of each semester by the Programming Committee, and is responsible for organizing
community service events throughout each term.
This brother is required to be on campus all semester and cannot be the
President, Programming Chairman, chair of another committee, or officer.
These events include, but are not limited to, the 3 events per term that span at
least 2.5 hours each as referred to in
Section~\ref{sec:community-service-event-planning}, as well as working with
brothers who cannot attend these events as outlined in
Section~\ref{sec:completion-of-hours}.
In addition to this, they are responsible for making sure each brother has
completed his required hours, and at their discretion may refer a brother to Kai
if their community service hours have not been completed.

\subsection{Community Service Event Planning}
\label{sec:community-service-event-planning}

The Community Service Chair and the Programming Committee will be responsible
for establishing 3 community service events lasting 2.5 hours or longer during
each term.
These events must be established and presented to the rest of the brothers at
the start of each term.
At least one of these events must be on a different day of the week than the
other two as to accommodate all brothers.

\subsection{Completion of Hours}
\label{sec:completion-of-hours}

Brothers are required to attend 2 of the 3 larger community service events
mentioned in Section~\ref{sec:community-service-event-planning}.
If they cannot do this they must let the Community Service chair know ahead of
time so that they can work with them to complete their requirements.

\subsection{Procedure for Incompletion of Service}
\label{sec:procedure-for-incompletion-of-service}

If the brother does not meet any one of these requirements then they must follow
the procedure outlined in the Attendance and Accountability Policy, listed under
Item~\ref{cha:attendance-and-accountability-policy},
Section~\ref{sec:inability-to-fulfill-brotherly-duties}.
If the semesters that the brother does not complete his hours are
non-consecutive then all three steps outlined in
Item~\ref{cha:attendance-and-accountability-policy},
Section~\ref{sec:inability-to-fulfill-brotherly-duties} must be followed
through.
If the semesters of non-completion are consecutive then Kai is allowed to vote
for Trial by Chapter on the second offense.

\section{Risk Management}
\label{risk-management}

Each brother must follow the Risk Management and Alcohol policies for both this
chapter and the general fraternity.

