\part{Articles}

\chapter{Chapter Summary}
\label{cha:chapter-summary}

\section{Name}
\label{sec:name}

The name of the Fraternity chapter shall be the Eta Tau chapter of Beta Theta
Pi.

\section{Purpose}
\label{sec:purpose}

Its objects shall be the same as those set in the Code of Beta Theta Pi
Fraternity (Article 1 Section 2) and this chapter's mission statement.

\section{Mission Statement}
\label{sec:mission-statement}

The Eta Tau chapter of Beta Theta Pi shall:
\begin{itemize}
	\item Promote the moral and social development of its members
	\item Develop each individual into proactive leaders
	\item Encourage the cultivation of intellect and ties to the fraternity's
		values
	\item Foster mutual assistance in the honorable labors and aspirations of
		life
	\item Recognize devotion to unsullied friendship and unfaltering fidelity as
		objects worthy of the highest aim and purpose of associated effort
\end{itemize}

\section{Governing Guidelines}
\label{sec:governing-guidelines}

This chapter shall be governed:
\begin{itemize}
	\item By this edition of the chapter’s Constitution and Bylaws
	\item By the Code of the General Fraternity of Beta Theta Pi
	\item By the laws of the Interfraternity Council of the Worcester
		Polytechnic Institute
	\item By the policies of Worcester Polytechnic Institute
	\item By all federal, state, and local laws
\end{itemize}

\chapter{Membership Qualifications and Expectations}
\label{cha:membership-qualifications-and-expectations}

\section{Membership Qualifications}
\label{sec:membership-qualifications}

Membership shall be conferred only upon male students of Worcester Polytechnic
Institute who have met the qualifications set out in Article II of the Code of
Beta Theta Pi ordained ``Membership''.
The aforementioned must also fulfill such additional scholastic requirements as
may be prescribed by this Constitution or by this chapter’s Bylaws.

\subsection{Zero Tolerance Policy for Harassment and Discrimination} 
\label{sec:zero-tolerance-policy-for-harassment-and-discrimination}

The Beta Theta Pi chapter will not discriminate against individuals based upon
race, age, citizenship, origin, ancestry, religion, disabilities, sexual
orientation, or marital status.

\section{Expectations}
\label{sec:expectations}

All brothers are expected to maintain good standing, as defined in the Bylaws,
and uphold these essential expectations:
\begin{itemize}
	\item Live by the five core values: Integrity, Intellectual Growth, Mutual
		Assistance, Trust, and Responsible Conduct
	\item Work towards the betterment of the brotherhood
	\item Open communication
	\item Fulfillment of the chapter's financial obligations
	\item Proactive involvement in the lives of the brothers and the activities
		of the brotherhood
\end{itemize}

\chapter{Meetings}
\label{cha:meetings}

\section{Chapter Meetings}
\label{sec:chapter-meetings}

Regular meetings of this chapter shall be held each week during the school year
as determined by the President.

\section{Special Meetings}
\label{sec:special-meetings}

Special meetings may be called by the President, executive board, and members
according to the Bylaws of this chapter.

\section{Robert's Rules of Order}
\label{sec:roberts-rules-of-order}

Robert's Rules of Order shall govern the meetings of this chapter in all cases
in which they apply and where they are not inconsistent with the Constitution of
Beta Theta Pi and the Constitution and Bylaws of this chapter.

\chapter{Chapter Organization}
\label{cha:chapter-organization}

\section{Executive Board}
\label{sec:executive-board}

The executive board shall be chaired by the President and composed of the
Communications Chairman, the Finance Chairman, the Brotherhood Chairman, the
Recruitment Chairman, the Education Chairman, the Programming Chairman, the Risk
Management Chairman, and all other Officers.
All executive board positions are elected positions.

\subsection{Purpose and Guidance}
\label{sec:purpose-and-guidelines}

The purpose of the executive board is to prepare business to ensure orderly
chapter meetings, to facilitate the operation of the chapter, to aid in the
control of chapter finances, to understand and report the condition of the
chapter, and to provide a business-like administration of chapter affairs and
policies.

\subsection{Duties of Officers}
\label{sec:duties-of-officers}

Further duties of the Officers are prescribed, but not finalized in the appendix
of this Constitution and are adjustable according to the voting procedure.

\subsection{Accountability}
\label{sec:accountability}

All brothers have the right to question the actions and decisions of the
executive board and have these concerns addressed.

\section{Committees}
\label{sec:committees}

The chapter is divided into the following committees each chaired by their
respective officer: 

\begin{itemize}
	\item Brotherhood
	\item Communication
	\item Finance
	\item Programming
	\item Education
	\item Risk Management
	\item Recruitment
\end{itemize}

Other committees may be proposed by the executive board and approved by the
chapter per the voting procedure.

\subsection{Scheduled Meetings}
\label{sec:committee-scheduled-meetings}

All committees will meet regularly as determined by their respective officer.

\section{Advisors}
\label{sec:advisors}

Every executive officer shall have an associated advisor; the chapter counselor
shall serve as the advisor to the President.

\subsection{Scheduled Meetings}
\label{sec:advisory-board-scheduled-meetings}

The Advisory Board shall meet at least once each semester to check in on the
status of the chapter and provide support for any undergraduate member as need
be.
Each Advisor should meet with their corresponding officer regularly.

\subsection{Advisor Qualifications}
\label{sec:advisor-qualifications}

There must be at least one Faculty Advisor whose position must be a volunteer
faculty/staff member from the Worcester Polytechnic Institute.
All other advisors can be either faculty/staff members from the Worcester
Polytechnic Institute or any qualified man or woman.
The District Chief of the General Fraternity will appoint these advisors with
the help of the chapter President.

\section{Other Chapter Officers}
\label{sec:other-chapter-officers}

Additional Chapter officers consist of:

\begin{itemize}
	\item Chorister
	\item Historian
	\item House Manager
	\item Parliamentarian
\end{itemize}

Other offices may be adopted or removed by the inclusion of a Bylaw change.

\subsection{Duties}
\label{sec:duties}

Duties of these officers are prescribed, but not finalized in the appendix of
this Constitution.
These duties can be adjusted by the executive board per the voting procedure.

\section{Kai Cabinet}
\label{sec:kai-cabinet}

The functions of the Kai Cabinet shall be to promote deeper relationships built
on trust and accountability among the brotherhood, to assure that areas of need
are identified, to have violations of ideals and policies tackled, and to hold
members accountable for actions deemed unworthy.
Members of the Kai Cabinet are elected per the voting procedure.

\subsection{Discipline of Members}
\label{sec:discipline-of-members}

The Kai Cabinet shall be responsible for pursuing all disciplinary action
against brothers not in good standing.

\subsection{Kai Training}
\label{sec:kai-training}

Each semester the Parliamentarian shall hold a training class on the
Constitution, the Bylaws, and disciplinary actions for the Kai Cabinet.

\subsection{Executive Officer Review}
\label{sec:executive-officer-review}

All officers elected to positions shall be reviewed and evaluated by the Kai
Cabinet at the end of the spring semester.

\chapter{Financial Operations}
\label{cha:financial-operations}

\section{Dues}
\label{sec:dues}

Dues shall be collected every semester from each member to fulfill the financial
obligations of the chapter and shall be payable as provided in the Bylaws.

\section{Financial Restrictions}
\label{sec:financial-restrictions}

The chapter is strictly forbidden from applying for, obtaining, or using any
money that the chapter does not have in its Billhighway or Venmo account
(\texttt{@BetaWPI}), except for reimbursements and emergency funds from
Interfraternity Council.
This applies particularly to loans of any sort.

\subsection{Barred Purchase of Alcohol}
\label{sec:barred-purchase-of-alcohol}

No money from dues or any other money of the chapter shall be used to purchase
alcoholic beverages.

\chapter{Risk Management}
\label{cha:risk-management}

\section{Commitment to Responsible Conduct}
\label{sec:commitment-to-responsible-conduct}

Beta Theta Pi recognizes that college students use and consume illicit drugs and
alcohol.
These substances have the potential for abuse if not used properly.
Beta Theta Pi does not condone the use of illicit substances or the act underage
drinking.
Our organization believes that Men of Principle should consume alcohol
responsibly and act in a manner that aligns with our values.

\section{Education}
\label{sec:education}

We are committed to ensuring brothers are properly educated on the topics of
alcohol and illicit drugs.
Further information can be found in the bylaws.

\section{Housing}
\label{sec:housing}

Any and all Beta Theta Pi houses shall be dry facilities that are completely
void of alcohol and illicit substances.
Brothers and new members shall abide by the house policy.

\chapter{Ceremonies}
\label{cha:ceremonies}

\section{Ritual Ceremonies}
\label{sec:ritual-ceremonies}

All ritual ceremonies will be conducted strictly in accordance with the Ritual
of Beta Theta Pi.

\section{Non Ritual Ceremonies}
\label{sec:non-ritual-ceremonies}

For a ceremony involving friends of Beta to bear the stamp of the fraternity it
must be approved by the chapter per its own definition in the Bylaws.

\chapter{Changes to the Constitution and Bylaws}
\label{cha:changes-to-the-constitution-and-bylaws}

\section{Amendments}
\label{sec:amendments}

The Constitution and Bylaws can be amended according to the voting procedure.
Amendments to the Constitution should address restatements of goals or purposes.
Amendments to the Bylaws should address procedural changes.
Brothers must be given sufficient time to review proposed changes to the
Constitution or Bylaws.

\section{Suspension of Bylaws}
\label{sec:suspension-of-bylaws}

The Bylaws may be suspended temporarily by a two-thirds supermajority vote with
prior notice or by a unanimous vote without prior notice according to the voting
procedure and reinstated according to the same procedure.

