\bylaw{Attendance and Accountability Policy}

\section{Inability to Fulfill Brotherly Duties}
If the brother does not meet any one of the requirements as listed in the Code of Conduct, Item 1, the respective Chairman must meet with the brother to have them explain the reason the requirement was not met.
Should the Chairman not find a valid reason, then the chapter must follow the steps listed:

\begin{itemize}
\item Before 1st Offense: The respective Chairman and Kai must have a discussion with the brother concerning the duty they are not completing to discuss the importance of their participation and steps to improving in the future.
Kai may issue an offense if they deem it necessary.

\item After 1st Offense: The brother must be brought before Kai with the respective Chairman to explain his position.
Kai must explain the importance of the duty that the brother is not fulfilling and stress that non-completion can result in Trial by Chapter.
They must also discuss steps so that the brother may improve in the future.
Kai may issue an offense if they deem it necessary.

\item After 2nd Offense: The brother is again brought before Kai to explain his position.
Kai must again explain the importance of the duty that the brother is not fulfilling.
Kai can also rule for Trial by Chapter if they deem it necessary.

\end{itemize}
Additionally, Kai does not have to issue an offense if they feel the brother has a valid excuse for not following through with the requirements mentioned above in Item 1, Section 4.
However, once an offense has been issued it cannot be revoked.

\section{Late Policy}

Late shall be defined as arriving to any event after the President, parliamentarian, or other appointed officer has called the meeting to order.
Arriving past the start of the event shall result in an unexcused absence.

This policy will not apply if the member has provided notice to the Communications Chairman or other respective chairman before the start of the meeting that he (the member) will be late to the meeting.
The notice must also include a reason for the member’s late arrival.
It will be left to the discretion of the respective Chairman to decide if the reason provided is valid.

