\chapter{Financial Operations}
\label{cha:financial-operations-bylaws}

\section{Price of Dues}

Dues will be set at \$500 per semester per person for spring 2018 dues, not
including fees from Billhighway.
In the fall semester of every year that is divisible by three (e.g. 2019, 2022,
2025, etc.), the Finance Committee will review this amount and adjust it solely
to account for any and all inflation that has occurred in the U.S. economy
since the last adjustment.
The price of dues shall remain constant unless changed in this way or by a
temporary emergency dues plan (see Sub-Section~\ref{sec:emergency-adjustments}).

\subsection{Emergency Adjustments to the Price of Dues}
\label{sec:emergency-adjustments}

The Finance Committee can draft a temporary emergency dues plan if the price of
dues needs to be changed because of an unforeseen emergency situation.
This plan must be discussed by the Executive Board and brought before the
chapter for discussion and voting.
The plan must be approved by the chapter as per the voting procedure to take
effect.
Temporary emergency dues plans may only be in effect for one semester, and must
be renewed by the chapter as outlined by the voting procedure at the end of
each semester.

\section{The Budget}
\label{sec:the-budget}

In the fall semester of 2017, and each subsequent year that is divisible by
three, the Finance Committee will assign a fall percentage and a spring
percentage to each of the following categories, such that the sum of all the
percentages for each semester (fall or spring) is 100\%:
\begin{itemize}
    \item President 
    \item Brotherhood Committee
    \item Communication Committee
    \item Finance Committee
    \item Programming Committee
    \item Education Committee
    \item Risk Management Committee (including housing)
    \item Recruitment Committee
    \item Savings
\end{itemize}
The designated percentage of the chapter’s total income
from dues for each semester will be allocated to the category.
These percentages will be presented to the Executive Board by the Finance
Chairman at or before the last Executive Board meeting of the first term of
each semester (A and C terms).

\subsection{Drafting the Budget}

The President and the Chairmen of each Committee shall present a proposed plan
for how to use the funds allocated to them or their Committee to the Executive
Board by the second Executive Board meeting of the second term of each semester
(B and D terms).

\subsection{Approving the Budget}

After discussion by the Executive Board, all of the plans proposed for the use
of allocated funds (the budget) will be presented to the chapter and voted on
as per the voting procedure.
In B term, this vote shall occur after Induction.
If the budget does not pass, the Finance Committee and Executive Board will
revise the budget until it is passed by the chapter.

\subsection{Adjustment to the Budget}

If an Executive Officer wants the percentages allocated to each category to be
changed between the ordinary re-evaluations in each year divisible by three
(see Item~\ref{cha:financial-operations}, Section~\ref{sec:the-budget}), he may
present an alternative percentage distribution to the Finance Committee.
The Finance Committee will approve or deny the alternative percentage
distribution within one week.
If it is approved, the alternative percentage distribution will be discussed by
the Executive Board and presented to the chapter with the next semester’s
budget.
It will be approved or denied by the chapter as a part of the next semester’s
budget.

\subsection{Prohibited Uses of Budgeted Funds}

Funds allocated in the manner described in this section shall not be used for
any Prohibited Use unless either a) such use is clearly denoted in the budget
approved by the chapter and this Sub-Section was specifically referenced when
the budget was debated by the chapter, as reflected in the minutes; or b) such
use is approved by a super-majority vote of the chapter after the budget is
passed.
The Prohibited Uses are: 
\begin{itemize}
    \item donation of the funds
\end{itemize}

\section{Upper Level Funds Organization}

\subsection{Overview of Funds Organization}

All funds managed by the chapter shall be divided into three pools of money: a
chapter operations fund as defined in Section~\ref{sec:chapter-operations-fund},
a general savings account as defined in
Section~\ref{sec:general-savings-account}, and an emergency reserve fund as
defined in Section~\ref{sec:emergency-reserve-fund}

\subsection{Chapter Operations Fund}
\label{sec:chapter-operations-fund}

The purpose of the Chapter Operations fund is to hold the operating funds of the
chapter.  The operating funds are determined by the Budget.

Money shall not be withdrawn from the Chapter Operations fund for unbudgeted
items.

If there are any remaining funds in Chapter Operation Fund at the end of a
payment period, all remaining funds shall be emptied into the General Savings
Account or the Emergency Reserve Fund unless directed otherwise by the Finance
Committee.

\subsection{General Savings Account}
\label{sec:general-savings-account}

\begin{description}
    \item[Bucket] An official monetary goal comprising one or more goal items, a
    currently allocated amount, and goal amount.
\end{description}

The purpose of the General Savings Account is to hold funds that are allocated
to General Savings buckets.
The General Savings Account shall comprise a maximum of four buckets.
Buckets are established by a simple-majority chapter vote.
Once established, a bucket may not be removed unless either the bucket goal is
reached and the item is purchased, or the chapter votes to remove the bucket as
per the voting procedure.
The chapter may also vote to change the goal item of a
bucket without altering the allocated amount.
If a bucket is voted to be removed, or the full allocated amount is not used to
purcahse the bucket item, the remaining funds shall be allocated to any other
existing bucket by the method outlined in this section.
If no buckets exist and funds remain in the General Savings account, the
chapter shall have one week to create one or more new buckets.

This account shall never be used to fund unexpected costs unless the
Emergency Reserve Fund is empty.

\subsubsection{Bucket Allocation}
\label{sec:bucket-allocation}

When money is allocated to any General Savings bucket, brothers shall be
entitled to determine which bucket their share of the additions is put.
All contributions to the account must be allocated to one or more bucket.

\subsection{Emergency Reserve Fund}
\label{sec:emergency-reserve-fund}

The purpose of the Emergency Reserve Fund is to hold funds meant to be used by
the chapter during emergency situations which require payment to provide relief
or recovery from said situation.

Emergency situations include but are not limited to:
\begin{itemize}
    \item If the Chapter House can not be filled with residents
    \item Member(s) are facing a financial emergency and can not fulfill due
        payment
    \item Committee(s) that exceed the amount of money they were budgeted and
        excess funds from other committees can not fully cover the deficit
\end{itemize}

The Emergency Reserve Fund shall only be used to help our chapter's financial
needs and not those of its members.

\section{Reimbursements}

Reimbursements for individual brothers are at the discretion of the Finance
Chairman.
Reimbursements may be distributed by check or Venmo.
The Finance Chairman shall make his best effort to distribute approved
reimbursements within one week of their request.

\subsection{Reimbursement Denial Appeals}

If a brother believes he deserves a reimbursement for a legitimate expenditure,
and the Finance Chairman denies him a reimbursement, he may appeal the denial.
The brother may appeal to the Kai Cabinet.
The Kai Cabinet shall hear the brother’s case, including input from the Finance
Committee, and vote to determine whether the brother deserves a reimbursement.
If the reimbursement is approved by the Kai Cabinet, the Finance Chairman shall
give the reimbursement to the brother within one week.

\section{Venmo}

The official Venmo account of the Eta Tau chapter of Beta Theta Pi shall be
\texttt{@BetaThetaPiWPI}.
Venmo may be used to collect payments other than dues from brothers or to
distribute reimbursements.
Any money in the official Venmo account must be transferred to Billhighway by
the end of each semester.
The Finance Chairman and President shall have control of the chapter Venmo
account, and may allow other brothers to temporarily have access to the chapter
Venmo account at their discretion.

