\chapter{The Payment Policy}
\label{cha:the-payment-policy}

\section{Billing Procedure}

Dues shall be charged at the beginning of each semester and must be paid in
full within two weeks from the day of billing unless an extension is granted by
the Finance Chairman.
This includes all initiation fee, induction or pledge fee, insurance fee,
heritage fee, membership fee, local dues, and any form of other fee billed from
the Billhighway payment platform.

\section{Billing Due Dates}

The chapter shall be made aware of the due date for each billed fee before the
fee is billed. 

\section{Timeline for Dues}

The member fee and the local dues shall be billed to brothers within the first
two weeks of the semester.
Potential New Members shall be made aware about the semester payment plan two
weeks before the Induction Ceremony.
Potential New Members shall be billed the induction fee immediately after the
Induction Ceremony.
Three weeks after the Induction Ceremony, the new member will be billed with
the initiation fee.
First-time local dues will be billed two weeks after the Initiation Ceremony.

\section{Unpaid Dues}

The Finance Chairman shall have a conversation with any member who has not paid
their dues by the deadline.
Fines shall be placed upon a delinquent brother as per the following timeline:

\subsection{Missed Payment Fine}

If the due date for a payment is missed, a \$10 fine shall be placed within 24
hours.
A further charge of \$10 shall be charged every two weeks until the payment is
made or arranged with the Finance Chairman.

\subsection{Trial by Chapter for Unpaid Dues}

If a brother has not paid his dues a month after the due date, then the brother
may be placed on a suspension period through Trial by Chapter.

