\chapter{Risk Management Policy}
\label{cha:risk-management-policy}

\section{Guiding Policies}

All brothers will adhere to the Risk Management Policies of the General
Fraternity of Beta Theta Pi and Worcester Polytechnic Institute.
In addition, all brothers will follow local, state, and national laws and
regulations.
All brothers shall abide by the General Fraternity of Beta Theta Pi and
Worcester Polytechnic Institute Anti-Hazing Policies.

\section{Housing}

All chapter houses shall be dry facilities free from the presence of alcohol
and illicit substances.
All brothers will abide by the Housing Rules of the chapter.

\section{Guidelines for All Official Chapter-Sponsored Social Functions}

\subsection{General Rules}

All official chapter sponsored social functions are planned by the Programming
Chairman and approved by the President and Risk Management Chairman.
All functions must follow the Risk Management Policy of Beta Theta Pi.
There must be a minimum of 1 “Sober guest monitors” per 15 people, at all
chapter socials.
All chapter functions are not to exceed three times the chapter size at social
functions; for other functions no guests are allowed, without prior approval of
the person responsible for the event.
The term ‘guest’ also excludes any member on any kind of probationary or
suspended status.
If the Maximum Capacity as determined by the Fire Code is less than three times
the size of the chapter, that shall be deemed the maximum amount of attendees
at a function.

\subsection{Rules for Guests and Members}
\begin{itemize}
    \item The management of the location where the function is being held has
        ultimate control of the function.  It is the responsibility of the
        Programming Chairman to stay in contact with them throughout the
        duration of the function.
    \item No alcohol may be brought into any function.
    \item The sober guest monitors, President, Risk Management Chairman, and
        Programming Chairman reserve the right to stop the consumption of
        alcohol by a member or guest and/or ask them to leave.
    \item Each member is responsible for his guest(s) and can be held
        accountable for the actions of their guest.
    \item Any member found violating the risk management policies of Eta Tau
        Chapter or Beta Theta Pi can and will be brought before Kai Cabinet for
        behavior review.
\end{itemize}

\section{Crisis Management}

In the event of a crisis the chapter will follow the Crisis Management Guide of
the General Fraternity which can be found in the Risk Management Manual.

\section{Zero Tolerance Policy for Hazing and Sexual Misconduct}

As per the General Fraternity’s Risk Management Policy, this chapter has a zero
tolerance policy towards any form of hazing, sexual assault, or sexual
harassment.

