\chapter{Duties of Executive Chairmen}
\label{app:duties-of-executive-chairmen}

\section{Duties of All Chairmen}
\begin{itemize}
\item To serve on the executive board and chair their respective committees
\item To clearly communicate all events to the chapter and President as soon as possible.
\item To send in officer reports at the time designated by the President.
\item To adequately transition the succeeding officer and to follow up with the officer when need be over the following year.
\item To demonstrate Ritual Competency before their second semester if the officer was not required to do so before nomination.
\end{itemize}

\section{Duties of President}

\begin{itemize}
\item To call and preside over special and active chapter meetings.
\item To act as the chapter’s official delegate to the General Convention.
\item To appoint or nominate for election such individuals or Committees as he
deems necessary to assist him in carrying our chapter functions and policies.
The power of appointment and the power of dismissal are concurrent.
\item To preside at banquets and special dinners.
\item To represent the chapter at interfraternity functions, campus fraternal
activities and any other occasions of similar nature.
\item To serve as the chapter’s delegate for the Interfraternity Council.
\begin{itemize}
\item In the case that the President is unable to attend the meetings for the
Interfraternity Council, he may appoint another brother to represent the
chapter in his stead.
\end{itemize}
\item To act as a liaison between the chapter and its advisors.
\item To coordinate the development of the chapter’s goals at the beginning of
the school year and/or report on the status of the chapter in the annual report
at the end of the academic year.
\item To ensure each chapter Chairman is properly performing his duties.
\item To organize the study of the chapter Constitution and Bylaws to ensure
they accurately represent the goals and operations of the chapter at least once
during his term.
\item To serve as Chair of executive board meetings.
\item To maintain and uphold the relevancy and importance of the ritual in all
chapter activities.
\item To prepare the chapter’s annual financial budget in conjunction with the
executive board, chapter Financial Advisor and the Finance Chairman.
\item To attend all chapter, alumni, and house corporation meetings.
\end{itemize}

\section{Duties of the Brotherhood Chairman}
\label{sec:duties-of-the-brotherhood-chairman}

\begin{itemize}

\item To serve as Chair of the Kai Cabinet.
\item To preside at an active meeting with the absence of the President.
\item To act as President in case of temporary absence.
\item To ensure maximum attendance at Beta Theta Pi leadership development
opportunities.
\item To promote the involvement of brothers in the Interfraternity Council,
student government and other campus and local organizations.
\item To procure all ritual equipment.
\item To schedule an EoW once per semester.
\item To be responsible for ensuring that all songs and parts are known for
rituals.
\item To ensure that all rituals are performed with dignity and in correlation
with all General Fraternity, IFC, and state policies.
\item To schedule ritual rehearsals prior to all performances of the Ritual.
\item To ensure that ritual regalia are properly stored, secured and cared for.
\item To educate newly initiated members on the objects, emblems and insignia
following the formal initiation ceremony.
\item To ensure the adherence to prescribed procedures, performances, and
proper use of all ritual regalia and equipment at all ceremonies as prescribed
in Chapter VIII of the Laws of Beta Theta Pi.
\item To coordinate the alumni roles in the rituals.
\item To assign big brothers to pledges along with the Education Chairman and
Recruitment Chairman.
\end{itemize}

\section{Duties of the Communications Chairman}
\label{sec:duties-of-the-communications-chairman}

\begin{itemize}

\item To send annual reports and correspondence to the Administrative Office
and University.
\item To assume the role of the President in the absence of both the President
and the Brotherhood Chairman.
\item To send articles to ‘The Beta Theta Pi’ magazine due, along with
photographs when appropriate.
\item To read important correspondences to the chapter at chapter meetings and
advise the President of such correspondence.
\item To initiate and answer general chapter correspondence which is not
specifically concerned with another chapter office.
\item To manage the chapter’s social media presence.
\item To send shingle orders, notice of admission, new member cards and
initiation forms to the Administrative Office within one week after pledging or
initiation.
\item To maintain the Alumni network.
\end{itemize}

\section{Duties of the Programming Chairman}
\label{sec:duties-of-the-programming-chairman}

\begin{itemize}

\item To schedule and organize all chapter social activities. 
\item To register all pertinent chapter social functions with the appropriate university office. 
\item To enforce all general fraternity risk management policies and campus regulations during chapter social functions. 
\item To maintain discipline at all chapter social functions and to coordinate the sober monitors and sober drivers with the chairman of Risk Management prior to the event. 
\item To inform all active members and pledges of chapter social events, including the posting of the programming calendar. 
\item To organize at least one alcohol free social event during the academic semester.
\item To be responsible for the organization of the chapter’s community service and philanthropic events.
\item To coordinate the chapter’s support and participation in other community service and philanthropic events on campus, particularly ones sponsored by fraternities and sororities.
\item To apply for the John Holt Duncan Service Award.
\item To record the weekly Community Service hours of the chapter members.
\end{itemize}

\section{Duties of the Education Chairman}
\label{sec:duties-of-the-education-chairman}

\begin{itemize}

\item To conduct the new member education program within all general
fraternity, campus and state guidelines. 
\item To schedule and preside over all new member meetings. 
\item To be responsible for the education of new members in Beta lore and
music.  \item To be responsible for the overall operation of the New Member
program according to current chapter practices.
\item To act as the liaison between the new members and the chapter.
\item To encourage the pledges’ interest and enthusiasm with regard to the new
member program and chapter activities.
\item To ensure that new members are never with brothers while in the presence
of alcohol or other drugs.
\item To be responsible for the scheduling of initiation, the pledging
ceremony, ordering new member pins and paddles and the selection of big
brothers in coordination with the Brotherhood Chairman. 
\item To work to ensure that at least 90\% of men formally pledged are
initiated. 
\item To complete the new member program by the start of the semester and
submit it for the approval of District Chief and Educator Advisor. 
\item To provide all bidded recruits with all of the materials they need for
the pledging process at the Tap In ceremony.
These materials include, but are not limited to:

\begin{itemize}

\item The Son of the Stars pledge book.
\item The completed new member program approved by the District Chief and
Education Advisor.
\item Music songbooks and CDs.
\end{itemize}

\item To assign big brothers to new members along with the Recruitment Chairman
and Brotherhood Chairman. 
\end{itemize}

\section{Duties of the Recruitment Chairman}
\label{sec:duties-of-the-recruitment-chairman}

\begin{itemize}

\item To reply and keep on file all recruitment recommendations in the form of
correspondence from alumni of this or any other chapter.  \item To maintain a
list of all potential members the chapter may be interested in at all times and
to present this list at a chapter meeting when appropriate.
\item To coordinate the chapter’s Men of Principle Scholarship effort. 
\item To oversee all recruitment related activities and to inform all active
members of acceptable recruitment practices. 
\item To ensure that all recruitment events are alcohol free. 
\item To be familiar with the institution and Interfraternity Council
recruitment regulations and to present to the chapter these regulations and all
other pertinent information deemed necessary for successful recruitment.
The Mission of the Beta Theta Pi Fraternity is to develop men of principle for
a principled life. 
\item To develop a recruitment calendar of events and distribute this calendar
to all members of Beta Theta Pi. 
\item To transition the recruits who receive a bid to the new member program.
\item To assign big brothers to pledges along with the Education Chairman and
Brotherhood Chairman.
\end{itemize}

\section{Duties of the Finance Chairman}
\label{sec:duties-of-the-finance-chaiman}

\begin{itemize}
\item To prepare the chapter’s annual financial budget in conjunction with the chapter Financial Advisor and President. 
\item To issue bills at the beginning of each billing period and to collect payments. 
\item To pay all bills promptly
\item To present the financial records of the chapter in good working order. 
\item To submit the names of members delinquent in paying their bill to the President/Kai Cabinet. 
\item To monitor and control each officer’s use of his portion of the budget 
\item To draft and update a promissory note to be signed by each undergraduate chapter member. 
\item To ensure that the chapter has an excellent financial rating from the assistant General Treasurer of Beta Theta Pi. 
\item To report the following balances at the first chapter of every term: 
\begin{itemize}

\item Chapter Account Balance 
\item Outstanding bills to the chapter
\item Outstanding dues to the chapter
\item Large upcoming expenses to the chapter
\item Status on organization registration forms 
\item Internal Revenue Service 990 EZ 
\item Worcester Polytechnic Institute Student Organization status 
\item Chapter Award Applications 
\item Membership rosters 
\item Housing rosters 
\end{itemize}
\item To submit financial statements to the chapter when asked. 
\item To update and manage the chapter’s financial profile.
\end{itemize}

\section{Duties of the Risk Management Chairman}
\label{sec:duties-of-the-risk-management-chairman}

\begin{itemize}

\item To ensure that Beta Theta Pi’s risk management policy is implemented at
each chapter event. 
\item To present risk management programs to the chapter at least once a term.
\item To submit all required risk management documentation to the
Administrative Office.
\item To make sure that a member of the Risk Management Committee is attending
meetings of the Programming and Brotherhood Committees.
\item To ensure that all brothers and new members are informed of the crisis
management policy.
\item To organize an alcohol awareness program for the chapter each year.
\item To assign sober monitors and sober drivers for the semester’s socials
planned by the Programming Chairman.
\item To schedule an annual fire/insurance inspection of chapter property.
\item To sign the paperwork to be the secondary house manager on the City of
Worcester lodging license.
\end{itemize}

