\chapter{Duties of Other Officers}
\label{app:duties-of-other-officers}

\section{Duties of All Officers}
\label{sec:duties-of-all-officers}

\begin{itemize}
\item Attend all executive board meetings.
\item Report to the executive board or relevant executive chairman regularly.
\end{itemize}

\section{Duties of the House Manager}
\label{sec:duties-of-the-house-manager}

\begin{itemize}

\item To work closely with the Risk Management Chairman.
\item To know Worcester/WPI/Beta National’s policies on Housing \& Living Quarters.
\item To coordinate the completion of weekly house duties.
\item To be responsible for the overall cleanliness of the chapter house.
\item To keep an updated list of needed repairs along with estimates of cost.
\item To order all cleaning supplies as needed.
\item To be responsible for the implementation of all house rules.
\item To act as a liaison to the Housing Corporation.
\item To sign the paperwork to be the primary house manager on the City of Worcester lodging license.
\item In the event that the House Manager will not be in the house over the summer, he must appoint a summer resident to sign the paperwork.
\end{itemize}


\section{Duties of the Chorister}
\label{sec:duties-of-the-chorister}

\begin{itemize}

\item To know all songs sung by the chapter.
\item To lead chapter in singing.
\item To teach selected songs to the chapter.
\item To organize singing practice sessions for Events that require songs.
\item To organize at least one serenade per semester.
\item To work closely with the Education Chairman to teach New Members songs.
\item To orchestrate the performance of the Loving Cup Ceremony.
\end{itemize}

\section{Duties of the Parliamentarian}
\label{sec:duties-of-the-parliamentarian}

\begin{itemize}

\item To call the chapter meeting of Beta Theta Pi to order.
\item To maintain order while the chapter meeting is in progress.
\item To know and assist in enacting Robert’s Rules of Order.
\item To maintain an updated copy of the Constitution and Bylaws.
\item To chair Trial by chapter.
\item To educate brothers as necessary on the Constitution and Bylaws.
\item To ensure that the Constitution and Bylaws are reviewed and understood by
both the executive board and the Kai Cabinet at least once a year.
\item To assist the chapter through any process that pertains to the amendment
of these Bylaws, or the chapter Constitution.
\end{itemize}

\section{Duties of the Historian}
\label{sec:duties-of-the-historian}

\begin{itemize}

\item To keep updated profiles on all current members and alumni in
coordination with the Communication Chairman.
\item To manage all chapter historic files and online documents in working
order.
\item To preserve chapter events via images and documentation.
\item To educate the chapter on relevant chapter history.
\item To keep and update family trees.
\item Responsible for the Composite and Graduation Materials.
\end{itemize}
