\chapter{Chapter Organization}
\label{cha:chapter-organization}

\section{Executive Board}
\label{sec:executive-board}

The executive board shall be chaired by the President and composed of the
Communications Chairman, the Finance Chairman, the Brotherhood Chairman, the
Recruitment Chairman, the Education Chairman, the Programming Chairman, the Risk
Management Chairman, and all other Officers.
All executive board positions are elected positions.

\subsection{Purpose and Guidance}
\label{sec:purpose-and-guidelines}

The purpose of the executive board is to prepare business to ensure orderly
chapter meetings, to facilitate the operation of the chapter, to aid in the
control of chapter finances, to understand and report the condition of the
chapter, and to provide a business-like administration of chapter affairs and
policies.

\subsection{Duties of Officers}
\label{sec:duties-of-officers}

Further duties of the Officers are prescribed, but not finalized in the appendix
of this Constitution and are adjustable according to the voting procedure.

\subsection{Accountability}
\label{sec:accountability}

All brothers have the right to question the actions and decisions of the
executive board and have these concerns addressed.

\section{Committees}
\label{sec:committees}

The chapter is divided into the following committees each chaired by their
respective officer: 

\begin{itemize}
	\item Brotherhood
	\item Communication
	\item Finance
	\item Programming
	\item Education
	\item Risk Management
	\item Recruitment
\end{itemize}

Other committees may be proposed by the executive board and approved by the
chapter per the voting procedure.

\subsection{Scheduled Meetings}
\label{sec:committee-scheduled-meetings}

All committees will meet regularly as determined by their respective officer.

\section{Advisors}
\label{sec:advisors}

Every executive officer shall have an associated advisor; the chapter counselor
shall serve as the advisor to the President.

\subsection{Scheduled Meetings}
\label{sec:advisory-board-scheduled-meetings}

The Advisory Board shall meet at least once each semester to check in on the
status of the chapter and provide support for any undergraduate member as need
be.
Each Advisor should meet with their corresponding officer regularly.

\subsection{Advisor Qualifications}
\label{sec:advisor-qualifications}

There must be at least one Faculty Advisor whose position must be a volunteer
faculty/staff member from the Worcester Polytechnic Institute.
All other advisors can be either faculty/staff members from the Worcester
Polytechnic Institute or any qualified man or woman.
The District Chief of the General Fraternity will appoint these advisors with
the help of the chapter President.

\section{Other Chapter Officers}
\label{sec:other-chapter-officers}

Additional Chapter officers consist of:

\begin{itemize}
	\item Chorister
	\item Historian
	\item House Manager
	\item Parliamentarian
\end{itemize}

Other offices may be adopted or removed by the inclusion of a Bylaw change.

\subsection{Duties}
\label{sec:duties}

Duties of these officers are prescribed, but not finalized in the appendix of
this Constitution.
These duties can be adjusted by the executive board per the voting procedure.

\section{Kai Cabinet}
\label{sec:kai-cabinet}

The functions of the Kai Cabinet shall be to promote deeper relationships built
on trust and accountability among the brotherhood, to assure that areas of need
are identified, to have violations of ideals and policies tackled, and to hold
members accountable for actions deemed unworthy.
Members of the Kai Cabinet are elected per the voting procedure.

\subsection{Discipline of Members}
\label{sec:discipline-of-members}

The Kai Cabinet shall be responsible for pursuing all disciplinary action
against brothers not in good standing.

\subsection{Kai Training}
\label{sec:kai-training}

Each semester the Parliamentarian shall hold a training class on the
Constitution, the Bylaws, and disciplinary actions for the Kai Cabinet.

\subsection{Executive Officer Review}
\label{sec:executive-officer-review}

All officers elected to positions shall be reviewed and evaluated by the Kai
Cabinet at the end of the spring semester.
